ShrinkNets: Learning Network Size while Training

### 2018-02-10 paper/ICML/evaluation.tex
typos

The results are shown in the top figure of \cref{figure_COVER}, with the two
optimization methods plotted as before. Here, {\it Static} method finds models
that perform well at a variety of sizes, because it is able to explore the
entire parameter space.  This is as expected;  the fact that \shrink perform
as well as the Static indicates that \shrink are doing an effective job of
exploring the parameter space using just the single $\lambda$ parameter.

Note that the best performing \shrink models has $96.91\%$ accuracy while the
best static model is only $96.66\%$ accurate, while the \shrink shrink model is $2.51$
times smaller. In addition, if we give up just 0.5\% error, \shrink find a
model that is 38.6 times smaller than any static network with equivalent accuracy.

@@

\begin{figure*}[t]\centering
\begin{minipage}{2.7in}
\centering
\includegraphics[width=\columnwidth]{CIFAR10_VGG_summary-arrows}
\vspace*{-10mm}
\caption{\label{figure_CIFAR10} Summary of the result of random
search over the hyper-parameters the \texttt{CIFAR10} dataset}
\vspace*{-5mm}
\end{minipage}
\begin{minipage}{.3in}
~~
\end{minipage}
\begin{minipage}{2.7in}
\centering\includegraphics[width=\columnwidth]{COVER_FC_summary-arrows}
\vspace*{-10mm}
\caption{\label{figure_COVER} Summary of the result of random
search over the hyper-parameters the \texttt{COVERTYPE} dataset
}
\vspace*{-5mm}
\end{minipage}
\end{figure*}

\begin{figure}[htb]
\begin{center}
\vspace{-.1in}
\includegraphics[width=.6\columnwidth]{size_evolution}
\vspace*{-5mm} 
\caption{ Evolution of the size of
  each layer over time (lighter: beginning, darker: end). On top a very large
  network performing $92.07\%$, at the bottom a simpler model with $90.5\%$
  accuracy. 
} 
\label{fig:network_size_evolution}
\end{center}
\vspace*{-4mm}
\end{figure}

@@

>>>>

The results are shown in the top figure of \cref{figure_COVER}, with the two
optimization methods plotted as before. Here, {\it Static} method finds models
that perform well at a variety of sizes, because it is able to explore the
entire parameter space.  This is as expected;  the fact that \shrink perform
as well as Static indicates that \shrink are doing an effective job of
exploring the parameter space using just the single $\lambda$ parameter.

Note that the best performing \shrink models have $96.91\%$ accuracy while the
best static model is only $96.66\%$ accurate, while the \shrink model is $2.51$
times smaller. In addition, if we give up just 0.5\% error, \shrink find a
model that is 38.6 times smaller than any static network with equivalent accuracy.

@@

\begin{figure*}[tb]\centering
\begin{minipage}{2.7in}
\centering
\includegraphics[width=\columnwidth]{CIFAR10_VGG_summary-arrows}
\vspace*{-10mm}
\caption{\label{figure_CIFAR10} Summary of the result of random
search over the hyper-parameters the \texttt{CIFAR10} dataset}
\vspace*{-5mm}
\end{minipage}
\begin{minipage}{.3in}
~~
\end{minipage}
\begin{minipage}{2.7in}
\centering\includegraphics[width=\columnwidth]{COVER_FC_summary-arrows}
\vspace*{-10mm}
\caption{\label{figure_COVER} Summary of the result of random
search over the hyper-parameters the \texttt{COVERTYPE} dataset
}
\vspace*{-5mm}
\end{minipage}
\end{figure*}

@@

\begin{figure}[h]
\begin{center}
\vspace{-.1in}
\includegraphics[width=.6\columnwidth]{size_evolution}
\vspace*{-5mm} 
\caption{ Evolution of the size of
  each layer over time (lighter: beginning, darker: end). On top a very large
  network performing $92.07\%$, at the bottom a simpler model with $90.5\%$
  accuracy. 
} 
\label{fig:network_size_evolution}
\end{center}
\vspace*{-4mm}
\end{figure}
